Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-21 referee.tex
Addressed results responses

At the time of the first star formation, our simulation only marginally resolves the smallest main halos, there is only a total of 6 halos above our resolution limit of $10^{5} M_{\odot}$. Because of this, there are not enough halos to accurately represent the HMF at that time, which is why we have not added that to Figure 2. We have added this detail to the first paragraph of the Results section.

\begin{referee}
S -- Figure 3 looks very nice. It would be helpful if an additional line that only 
provides the global LWBG (in units of J21) was included.
\end{referee}
Thank you for your comment. The global LWBG has been added as a red dashed line. More detail about the LW background (solid red line) has also been added.

\begin{referee}
T -- The authors find no correlation between the host halo mass and the Lyman-Werner background intensity. However, they only look at the LWBG flux at the time of Pop III formation - is there maybe a correlation between the time integrated LW flux?
\end{referee}
While the time integrated LW flux would be interesting to follow, and may provide some further insight to what we are exploring, this would be difficult to calculate. It would require constant tracking of halos through time to calculate the time integrated LW flux.

\begin{referee}
U -- Figures 7 and 8 show very nice histograms as an additional panel on the right.  I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
\end{referee}
The side histogram has been added to Figure 9.

>>>>

At the time of the first star formation, our simulation only marginally resolves (with 50 particles) the smallest minihalos that can host Pop III star formation. Thus there is only a total of 6 halos above our resolution limit of $10^{5} M_{\odot}$. Because of this lack of data, there are not enough halos to accurately represent the halo mass function at that time, which is why we have not added that to Figure 2.  However we have added some details about the number of halos and the redshift of the first star formation with the analytical expectation (one $10^5~M_\odot$ halo per comoving Mpc$^3$) to the first paragraph of the Results section.

\begin{referee}
S -- Figure 3 looks very nice. It would be helpful if an additional line that only 
provides the global LWBG (in units of J21) was included.
\end{referee}
Thank you for your comment. We have added the global LW background as a red dashed line. We have also added more details about the LW background (solid red line) to the text.

\begin{referee}
T -- The authors find no correlation between the host halo mass and the Lyman-Werner background intensity. However, they only look at the LWBG flux at the time of Pop III formation - is there maybe a correlation between the time integrated LW flux?
\end{referee}
While the time integrated LW flux would be interesting to follow, and may provide some further insight to what we are exploring, this would be difficult to calculate in post-processing with the information contained in the datasets. It would require constant tracking of halos through time to calculate the time integrated LW flux.

\begin{referee}
U -- Figures 7 and 8 show very nice histograms as an additional panel on the right.  I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
\end{referee}
We agree that this addition is useful and have added a side histogram to Figure 9.
